---
title: "Supplementary material"
subtitle: "Quantifying compositional differences in 24-hour sleep and wake architecture in individual with insomnia by sleep opportunity"
author: "Flora Le (flora.le@monash.edu)"
# date: "`r Sys.Date()`"
output: 
  cleanrmd::html_document_clean:
    mathjax: default
    theme: superstylin
    use_fontawesome: true
    toc: yes
    toc_float: yes
    collapsed: no
    smooth_scroll: no
    toc_depth: 4
    fig_caption: yes
    number_sections: true
---
```{=html}
<style>
body .main-container {
  max-width: 1200px;
}
table { font-size: 0.8rem; }
</style>
```

```{r, echo=FALSE, message=FALSE, include=FALSE}
source("supp.R")
knitr::opts_chunk$set(
  dev        = "svglite",
  dpi        = 100,
  fig.retina = 1,
  fig.width  = 5,
  fig.height = 5,
  fig.align  ='center'
)
```

*Notes* Short SO (P10), Medium SO (P25–P75 average), Long SO (P90). Bottom row is reference group; positive values indicate more time compared to reference and negative values indicate less. Percentages are relative to total sleep time. WD = wake during the day. SOL = sleep onset latency. N1+2 = NREM sleep stages 1 and 2 combined. N3 = NREM sleep stage 3. REM = rapid-eye-movement sleep. WASO = wake after sleep onset. SO = sleep opportunity.

## Main analysis
### Diagnostics
#### Rhat

```{r, echo=FALSE, message=FALSE, warning=FALSE}
rhat_vals <- brms::rhat(m_tib_isi1)
rhat_tbl <- data.frame(
  Parameter = names(rhat_vals),
  Rhat = as.numeric(rhat_vals),
  check.names = FALSE
)
```

```{r, message=FALSE, warning=FALSE}
# max r hat
max(rhat_tbl$Rhat)
# Parameters with R-hat > 1.01:
sum(rhat_tbl$Rhat > 1.01)
```

```{r, message=FALSE, warning=FALSE}
## Main predictors
so_min_rhat <- rhat_tbl[grepl("so_min", rhat_tbl$Parameter) & grepl("bs", rhat_tbl$Parameter), , drop = FALSE]
knitr::kable(so_min_rhat, digits = 3, caption = "R-hat for Sleep Opportunity parameters")
```

#### Posterior predictive check

```{r, message=FALSE, warning=FALSE, fig.width = 20, fig.height=5}
pp_plots <- lapply(c("z11", "z21", "z31", "z41", "z51"), function(i) {
  pp_check(m_tib_isi1, resp = i, ndraws = 100) +
    theme_minimal()
})
wrap_plots(pp_plots, nrow = 1)
```

### Main model summary

```{r, warning=FALSE}
summary(m_tib_isi1)
```

### Estimated 24h sleep-wake architecture composition by sleep opportunity
```{r, echo=FALSE, message=FALSE, warning=FALSE, out.width="110%"}
knitr::include_graphics(plot_min_perc_isi1)
```

```{r, warning=FALSE, echo=FALSE}
kbl(sup_tibq5_isi1_sum, espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, color = "#4F5D5B", background = "#ffffff")
```

## Stratified analysis
### Estimated 24h sleep-wake architecture composition by sleep opportunity
#### By Sex

```{r, echo=FALSE, results='asis'}
cat(
  "<strong>Female</strong>: &#9650; ",
  "<strong>Male</strong>: &#9660;"
)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, out.width="120%"}
knitr::include_graphics(plot_sex_min_perc_isi1)
```

```{r, warning=FALSE, echo=FALSE}
kbl(sup_tibq5_isi1_sex_sum, espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, color = "#4F5D5B", background = "#ffffff")
```

#### By Age

```{r, echo=FALSE, results='asis'}
cat(
  "<strong>Below 45y</strong>: &#9668;",
  "<strong>45y and above</strong>: &#9658;"
)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, out.width="120%"}
knitr::include_graphics(plot_age_min_perc_isi1)
```

```{r, warning=FALSE, echo=FALSE}
kbl(sup_tibq5_isi1_age_sum, espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, color = "#4F5D5B", background = "#ffffff")
```

#### By PSG type

```{r, echo=FALSE, results='asis'}
cat(
  "<strong>Home PSG</strong>: &#9632; ",
  "<strong>Lab PSG</strong>: &#9670;"
)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, out.width="120%"}
knitr::include_graphics(plot_serv_min_perc_isi1)
```

```{r, warning=FALSE, echo=FALSE}
kbl(sup_tibq5_isi1_serv_sum, espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, color = "#4F5D5B", background = "#ffffff")
```